---
title: "Spurs!"
author: "mleary"
date: "December 19, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: hide
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)

```

##Intent:

I am trying to pull Spurs football data from the FotMob website.  If successful, I might use this to then pull data for all EPL teams, but we will see.  I have tried this before, but wanted to start fresh and better document my approach.  My Goals for this  are (with some being stretch goals):

*  Scrape individual game data - final score, lineup
*  Scrape game facts - time of subs, who scored, who assisted, etc.
*  Go back for entire 2018-2019 EPL and structure data for each match (format TBD)
*  Automate process for future data pulls

## Approach:

### Initial Set up & Assesment

* I opted to go straight to the Spurs section on the FotMob website for ease. I will need to revisit this if I try to grab data for other teams as well.
* I used the Selector Gadget to assist in finding the correct sections
* I had some initial trouble getting the correct html_nodes.  I tried ".fm-team__fixtures" based on selector gadget but that did not appear to work.
```{r}
# Packages
library(tidyverse)
library(rvest)
library(XML)

 #Spurs Website
spurs.webaddress <- 'https://www.fotmob.com/teams/8586/'

spursTable <- read_html(spurs.webaddress) %>% 
  html_nodes("fm-team__list__item") #%>% 

```

* I decided to reverse my approach and work from lowest level on up.  I am going to scrape data for an invidual game and then work backwords

```{r}
single.game <- 'https://www.fotmob.com/livescores/2781956'

nufc.game <- read_html(single.game)

#
home.events <- read_html(single.game) %>% 
  html_nodes('.fm-match-event--home')

write_xml(nufc.game, file= 'temp.html')
```

* Looking at the HTML code, the details I want are buried in javascript at the bottom of the file.  I haven't worked with Javascript before and don't feel like trying to Google that soltuion.  This makes a lot of sense, and explains past failures.

### Changing Websites

* Due to the set up of the initial website, I am going to try another website and see if it is simpler.  Next attempt is with the actual Premiere League website.

```{r}
epl.site <- read_html('https://www.premierleague.com/match/38475') %>% 
  html_nodes('.timeLineContainer') 

write_xml(epl.site, file = 'temp2.html')
```

* New HTML file is cluttered, but looks like it will work (view Temp2 file in dev)

* I'll work on one match again to make sure I can pull data, and then work up to scraping multiple matches

* Ideally I want to also pull starting lineus along wiht Match data

```{r}
spurs.match <- read_html('https://www.premierleague.com/match/38475') %>% 
  html_nodes('.timeLineContainer')

event.info <- spurs.match %>% 
        # The relevant tag
        html_nodes('.eventInfo') %>% 
        html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()


min <- spurs.match %>% 
        # The relevant tag
        html_nodes('.min') %>% 
        html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()

playerinfo <- spurs.match %>% 
        # The relevant tag
        html_nodes('.eventPlayerInfo') %>% 
        html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()

team <- spurs.match %>% 
        # The relevant tag
        html_nodes('.team') %>% 
        html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()

```

* So I've found the nodes and started to understand the strucutre.  I don't want to repeat these chained operations, so I am going to try and create fucntions to pull the data. 

* I've also decided to start with lineups data, since it is identical for every game.  I want to pull this first and make sure I can apply it to multiple games..

```{r}

web.lineups <- spurs.match %>% 
  html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "matchLineupTeamContainer", " " ))] | //*[contains(concat( " ", @class, " " ), concat( " ", "matchTeamFormation", " " ))]')

#formation
homeformation <- web.lineups[1] %>% 
  html_text() 

awayformation <- web.lineups[3] %>% 
  html_text() 

#Lineups
homeLineup <- web.lineups[2] %>% 
  html_text() %>% 
  sub(pattern= "Substitutes.*", replacement = "")

web.lineups %>% html_text() %>% 
        # Trim additional white space
        str_trim() %>%                       
        # Convert the list into a vector
        unlist()

```

* After some initial attempts to just grab the entire fields and back into the lineup, I realized it was unwieldy.  I am pretty sure I need to create parsing functions, which I was trying to avoid.  Sigh.


### Sub Component - Create Parsing Function for Lineups

* After reviewng the EPL website, it seems to make sense to pull the lineup data seperataly and make that a function.

```{r}

xpath_lineups <- '//*[contains(concat( " ", @class, " " ), concat( " ", "matchLineupTeamContainer", " " ))] | //*[contains(concat( " ", @class, " " ), concat( " ", "matchTeamFormation", " " ))]'



## Testing one componet first
test <- web.lineups[[2]] %>% 
  html_nodes('.player') %>%
  html_text() %>% 
  #str_replace('[0-9]+[:punct:]', "") %>% 
  as.data.frame() %>% 
  mutate(Position = word(., 4),
         Name = word(., 2, 3),
         Number = word(., 1),
         Captain = ifelse(str_sub(Position, 1,1) == "C", TRUE, FALSE),
         Position = str_replace(Position, "C",""),
         Starter = ifelse(row_number() < 12,  TRUE, FALSE),
         Home_Away = "Home") %>% 
  select(-1)

scrape_lineups <- function(html.input, xpath.input){
  
  lineups <- list()
  html.input <- html.input %>% html_nodes(xpath = xpath.input)
  
  lineups$HomeFormation <- html.input[1] %>% html_text()
  lineups$AwayFormation <- html.input[3] %>% html_text()
  
  lineups$HomeLineup <-html.input[[2]] %>% 
    html_nodes('.player') %>%
    html_text() %>% 
    str_replace('[0-9]+[:punct:]', "") %>% 
    as.data.frame() %>% 
    mutate(Position = word(., -1),
           Name = word(., 2, -2),
           Number = word(., 1),
           Captain = ifelse(str_sub(Position, 1,1) == "C", TRUE, FALSE),
           Position = str_replace(Position, "C",""),
           Starter = ifelse(row_number() < 12,  TRUE, FALSE),
           Home_Away = "Home") %>% 
    select(-1) 
    
  lineups$AwayLineup <-html.input[[4]] %>% 
    html_nodes('.player') %>%
    html_text() %>% 
    str_replace('[0-9]+[:punct:]', "") %>% 
    as.data.frame() %>% 
    mutate(Position = word(., 4),
           Name = word(., 2, 3),
           Number = word(., 1),
           Captain = ifelse(str_sub(Position, 1,1) == "C", TRUE, FALSE),
           Position = str_replace(Position, "C",""),
           Starter = ifelse(row_number() < 12,  TRUE, FALSE),
           Home_Away = "Away") %>% 
    select(-1) 
  
  return(lineups)
}

print(scrape_lineups(spurs.match, xpath_lineups))
```

* Boom!  This worked, although I have made a mess of variables and organization I realized. I think I'll just create a src file once I work through everything, and keep this as exploration.

### Testing Scrape_Lineup Function for other matches

* Since I can succesfully pull the lineup data, I want to see if it works across multiple games before I move forward with the more complicated match data.

```{r}
test.match <- read_html('https://www.premierleague.com/match/38487') %>% 
  html_nodes('.timeLineContainer')

print(scrape_lineups(test_match, xpath_lineups))
##Success!

test_match <- read_html('https://www.premierleague.com/match/38486') %>% 
  html_nodes('.timeLineContainer')

print(scrape_lineups(test_match, xpath_lineups))

```

* This worked.  Added bonus, the url format for the EPL website is structured sequentially based on game, so it should be easy to iterate over a series matches!

* **Note I had to adjust my word() functions after I noticed that there are some players with 1 name.  I adjusted my indexing to grab the name as simply the middle word/words.**

* One note of caution, messing around EPL site and I found some odd pages ('https://www.premierleague.com/match/34000')

* I grabbed first match of 2018/2019 season while I was looking: 'https://www.premierleague.com/match/38313'


### Back to scraping Game Details
```{r}
spurs.match %>% 
  html_nodes('.eventInfo') %>% 
  html_nodes('.name') %>% 
  html_text()

spurs.match %>% 
  html_nodes('.eventInfo') %>%
  html_nodes('.name') %>% 
  html_text()

spurs.match %>% 
  html_nodes('.eventInfo') %>%
  html_nodes('.visuallyHidden') %>% 
  html_text() %>% 
  .[. != "Substitution On"] %>% 
  .[. != "Substitution Off"]

spurs.match %>% 
  html_nodes('.eventInfo') %>%
  html_nodes('.teamScore') %>% 
  html_text()


### Trying to pull all .eventInfo and then parse data - not fun
spurs.match %>%
  html_nodes('.eventInfo') %>% 
  html_text() %>% 
  as.data.frame() %>% 
  mutate(Time  = str_sub(., 1, regexpr("'", .)),
         Event = str_sub(., regexpr("'", .) + 1, regexpr("[A-Z]{3}", .) - 1),
         Score = str_sub(., regexpr("[A-Z]{3}", .), regexpr("[A-Z]{3}", .) + 13))
            
  
```

* After messing around, I think it will make sense to capture sub on/off time in lineup.  Starters will be assigened on at O minuntes.

* I also think it will make sense to create helper functions wiht the correct html_paths and pull the data that way - it will probably be cleaner in the long run.


### First attempt at putting it all together
```{r}

#Test match
match <- 38483

### Lineups Xpath
path.lineups <- '//*[contains(concat( " ", @class, " " ), concat( " ", "matchLineupTeamContainer", " " ))] | //*[contains(concat( " ", @class, " " ), concat( " ", "matchTeamFormation", " " ))]'

# Events CSS
path.events <- '.timeLineContainer'

matchlink <- paste0('https://www.premierleague.com/match/', match) %>% 
  read_html()
  
scrape_lineups <- function(match.page, path.lineups) {

    lineups <- list()
    match.page <- match.page %>% html_nodes(xpath = path.lineups)
    
    lineups$HomeFormation <- html.input[1] %>% html_text()
    lineups$AwayFormation <- html.input[3] %>% html_text()
    
    lineups$HomeLineup <-html.input[[2]] %>% 
      html_nodes('.player') %>%
      html_text() %>% 
      str_replace('[0-9]+[:punct:]', "") %>% 
      as.data.frame() %>% 
      mutate(Position = word(., -1),
             Name = word(., 2, -2),
             Number = word(., 1),
             Captain = ifelse(str_sub(Position, 1,1) == "C", TRUE, FALSE),
             Position = str_replace(Position, "C",""),
             Starter = ifelse(row_number() < 12,  TRUE, FALSE),
             Home_Away = "Home") %>% 
      select(-1) 
      
    lineups$AwayLineup <- html.input[[4]] %>% 
      html_nodes('.player') %>%
      html_text() %>% 
      #str_replace('[0-9]+[:punct:]', "") %>% 
      as.data.frame() %>% 
      mutate(Position = word(., 4),
             Name = word(., 2, 3),
             Number = word(., 1),
             Captain = ifelse(str_sub(Position, 1,1) == "C", TRUE, FALSE),
             Position = str_replace(Position, "C",""),
             Starter = ifelse(row_number() < 12,  TRUE, FALSE),
             Home_Away = "Away") %>% 
      select(-1) %>% 
      mutate(TimeOn = ifelse(Starter == TRUE, 0,
                        ifelse(length(str_extract(., '[0-9]+[:punct:]'))) > 0, str_extract(., '[0-9]+[:punct:]'), NA))
             
            # TimeOff = ifelse(TimeOn == NULL, NULL, "Test")
            #             #ifelse()))
            # 
    
    return(lineups)
}


test <- 
```


###General Notes

* I might want to update Starter column with two fields for On and Off, to address subs later
