---
title: "Spurs!"
author: "mleary"
date: "December 19, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: hide
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

##Intent:

I am trying to pull Spurs football data from the FotMob website.  If successful, I might use this to then pull data for all EPL teams, but we will see.  I have tried this before, but wanted to start fresh and better document my approach.  My Goals for this  are (with some being stretch goals):

*  Scrape individual game data - final score, lineup
*  Scrape game facts - time of subs, who scored, who assisted, etc.
*  Go back for entire 2018-2019 EPL and structure data for each match (format TBD)
*  Automate process for future data pulls

## Approach:

### Initial Set up & Assesment

* I opted to go straight to the Spurs section on the FotMob website for ease. I will need to revisit this if I try to grab data for other teams as well.
* I used the Selector Gadget to assist in finding the correct sections
* I had some initial trouble getting the correct html_nodes.  I tried ".fm-team__fixtures" based on selector gadget but that did not appear to work.

```{r}
# Packages
library(rvest)
library(dplyr)
library(tidyr)
library(XML)

#Spurs Website
spurs.webaddress <- 'https://www.fotmob.com/teams/8586/'

spursTable <- read_html(spurs.webaddress) %>% 
  html_nodes("fm-team__list__item") #%>% 

```

* I decided to reverse my approach and work from lowest level on up.  I am going to scrape data for an invidual game and then work backwords

```{r}
single.game <- 'https://www.fotmob.com/livescores/2781956'

nufc.game <- read_html(single.game)

#
home.events <- read_html(single.game) %>% 
  html_nodes('.fm-match-event--home')

write_xml(nufc.game, file= 'temp.html')
```

* Looking at the HTML code, the details I want are buried in javascript at the bottom of the file.  I haven't worked with Javascript before and don't feel like trying to Google that soltuion.  This makes a lot of sense, and explains past failures.

### Changing Website
* Due to the set up of the initial website, I am going to try another website and see if it is simpler.  Next attempt is with the Premiere League website.

```{r}
epl.site <- read_html('https://www.premierleague.com/match/38475') %>% 
  html_nodes('.timeLineContainer') 

write_xml(epl.site, file = 'temp2.html')
```

* New HTML file is cluttered, but looks like it will wor (view Temp2 file in directory.)
* I'll work on one match again to make sure I can pull data, and then work up to scraping multiple matches


```{r}
spurs.match <- read_html('https://www.premierleague.com/match/38475') %>% 
  html_nodes('.visuallyHidden')


#write_xml(spurs.match, file = 'temp3.html')
```



