---
title: "Spurs!"
author: "mbl"
date: "December 19, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Intent:

I am trying to pull Spurs football data from the FotMob website.  If successful, I might use this to then pull data for all EPL teams, but we will see.  I have tried this before, but wanted to start fresh and better document my approach.  My Goals for this  are (with some being stretch goals):

*  Scrape individual game data - final score, lineup
*  Scrape game facts - time of subs, who scored, who assisted, etc.
*  Go back for entire 2018-2019 EPL and structure data for each match (format TBD)
*  Automate process for future data pulls

## Approach:

### Initial Set up & Assesment

* I opted to go straight to the Spurs section on the FotMob website for ease. I will need to revisit this if I try to grab data for other teams as well.
* I used the Selector Gadget to assist in finding the correct sections
* I had some initial trouble getting the correct html_nodes.  I tried ".fm-team__fixtures" based on selector gadget but that did not appear to work.
```{r, echo = FALSE}
# Packages
library(rvest)
library(dplyr)
library(tidyr)
library(XML)

#Spurs Website
spurs.webaddress <- 'https://www.fotmob.com/teams/8586/'

spursTable <- read_html(spurs.webaddress) 


```



